% !TeX root = ../../cv_en_full.tex
% ===================== PUBLICATIONS ========================
\section{Publications}

\noindent\textit{Summary: XX peer-reviewed, XXXX citations (Google Scholar by \today)}

\noindent\small{%
  $\ddagger$: Student supervised by Dr.~[Your Name] \quad
  $\dagger$: Student co-supervised by Dr.~[Your Name] \quad
  *: Corresponding author%
}

\vspace{4pt}
\noindent\textbf{Book Chapters}
\begin{enumerate}[label={[B\arabic*]}, leftmargin=2.8em]
  \item Author 1, Author 2, and \textbf{Your Name},
        ``Chapter Title,''
        in \textit{Book Title}, Publisher, Year.
\end{enumerate}

\vspace{4pt}
\noindent\textbf{Journals}
\begin{enumerate}[label={[J\arabic*]}, leftmargin=2.8em]
  \item N. Tamami, \textbf{I. C. Ramadhan}, K. Alfathdyanto, Madyono, H. Hermawan,
        H. M. Rosalinda, A. W. R. Gusti, and W. Trisniani,
        ``Implementasi Media Informasi Berbasis Running Text untuk Meningkatkan
        Efisiensi dan Efektivitas Penyampaian Informasi di Kelurahan Keputih,''
        \textit{j-dinamika}, vol. 10, no. 2, pp. 254--260, Aug. 2025.

  \item \textbf{I. C. Ramadhan}, A. Hendriawan, and H. Oktavianto,
        ``YOLOv11-Based Detection of Indonesian Traffic Signs: Transfer Learning
        vs. From-Scratch Training,''
        \textit{Journal of Applied Informatics and Computing (JAIC)}, vol. 9,
        no. 4, pp. 1363--1373, Aug. 2025.
\end{enumerate}

\vspace{4pt}
\noindent\textbf{Conferences}
\begin{enumerate}[label={[C\arabic*]}, leftmargin=2.8em]
  \item \textbf{I. C. Ramadhan}, B. R. Trilaksono, and E. M. I. Hidayat,
        ``Towards Real-Time Graph Neural Network-Based 3D Object Detection
        for Autonomous Vehicles,''
        in \textit{Proc. 19th IEEE Int. Colloq. Signal Processing \& Its
        Applications (CSPA)}, Kedah, Malaysia, 2023, pp. 105--110.
\end{enumerate}
